\documentclass[sigconf,nonacm]{acmart}

\usepackage{booktabs} % For formal tables


% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

\begin{document}
\title{Evaluating the feasibility of bus crowd estimation\\ using Wi-Fi and Bluetooth}
%\titlenote{Produces the permission block, and  copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as \texttt{acmart.pdf} document}


\author{Anil Yelam}
\affiliation{%
  \institution{UC San Diego}
}
% \email{ayelam@ucsd.edu}

% \author{Aaron Shalev}
% \affiliation{%
%   \institution{UC San Diego}
% }
% \email{schulman@ucsd.edu}


\begin{abstract}
Public transportation is the most efficient of the 
transportation systems, especially in the dense 
metropolitan areas. With ever worsening traffic 
conditions, there has been a renewed push among city 
planners to improve the adoption of mass transit systems. 
To achieve this, improving passenger experience and optimal 
usage of resources is vital. Real-time estimation of 
congestion in buses can be used to improve user experience 
by dispersing this knowledge ahead of time. In longer the 
term, this information can also used for efficient 
scheduling of buses and optimal planning of bus routes 
in an area. In this paper, we evaluated the feasibility of 
using wireless signals originating from devices in a bus 
to develop low-cost, widely-deployable solutions for 
real-time crowd density estimation. We evaluated the 
accuracy of our solutions by performing experiments 
on MTS buses in San Diego, and we further explored 
limitations of these solutions. While the exact number 
of people cannot be estimated, this work shows that the 
Bluetooth and Wi-Fi data can be used to get a reasonable 
approximation of crowd density that could be used for the 
purposes of analyzing crowd transit patterns.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003106.10003119</concept_id>
  <concept_desc>Networks~Wireless access networks</concept_desc>
  <concept_significance>500</concept_significance>
  </concept>
 <concept>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[100]{Networks~Wireless access networks}



\maketitle

\input{body}

\bibliographystyle{ACM-Reference-Format}
\bibliography{bibliography}

\end{document}
